Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2016-11-23 paper.tex
Rename figure with prefix fig

\documentclass[aps,prd,twocolumn,superscriptaddress]{revtex4-1}
% Intended to be built with pdflatex, using the REVTEX 4.1 package.
% Template taken from FermiLab APS Jouranl template.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{affine_parameter_label}
  \caption{Affine parameterization of a neutrino trajectory of momentum
    $p_\alpha$.
    The fiducial observer with velocity $u^\alpha$ sits at $x^\alpha_o$,
    the neutrino emission event is at $x^\alpha_e$. The affine parameter
    increases from the emission event: $\lambda_e<\lambda'<\lambda''$.}
  \label{fig:affine_param}
\end{figure}

@@

\subsection{Dummy Tests}
[Maybe we don't need to present these tests, but make sure to establish
confidence in the basics:
gravitational redshift, Doppler shift, thermodynamic equilibrium.]
\todo{setup and run dummy tests}

\subsection{Homogenous Absorbing Star}
[Test described in~\cite[Sec.~3.2]{smit1997-two_moment}.]
\todo{Jerred: run test}

\subsection{Homogenous Scattering Star}
\todo{maybe drop this test}
[Test presented in~\cite{humm1971-grey_transfer}
and described in~\cite[Sec.~9.1.1]{abdi2012-monte_carlo}.
Our version would be a point source embedded in a spherical distribution
of purely elastic-scattering material. It requires an analytical estimate
of $J$.]
\todo{formulate analytic $J$.}

\subsection{Post-Bounce Neutron Core}
[Standard radiation transport test described in~\cite{ocon2015-gr1d_with_nu},
and in \cite[App.~E.6]{fouc2015-m1_nsbh},
and in~\cite{abdi2012-monte_carlo}.]
\todo{Evan: provide initial data and $H^r(\varepsilon)$}
\todo{Jerred: setup and run test}

\subsection{Disk Comparison to M1}
[Compute total and relative number and energy luminosities for a disk evolved
in one of~\cite{fouc2015-m1_nsbh, fouc2016-m1_nsns, fouc2016-m1_evolve_n}.
Expect agreement within factors of a few (?).]
\todo{code up moment integrals}
\todo{compute luminosities from M1}
\todo{compute luminosities from ray tracing}

>>>>

\documentclass[aps,floatfix,prd,superscriptaddress,twocolumn]{revtex4-1}
% Intended to be built with pdflatex, using the REVTEX 4.1 package.
% Template taken from FermiLab APS Jouranl template.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-affine_parameter_label}
  \caption{Affine parameterization of a neutrino trajectory of momentum
    $p_\alpha$.
    The fiducial observer with velocity $u^\alpha$ sits at $x^\alpha_o$,
    the neutrino emission event is at $x^\alpha_e$. The affine parameter
    increases from the emission event: $\lambda_e<\lambda'<\lambda''$.}
  \label{fig:affine_param}
\end{figure}

@@

\subsection{Dummy Tests}
\label{ssec:tests_basic}
[Maybe we don't need to present these tests, but make sure to establish
confidence in the basics:
gravitational redshift, Doppler shift,
geoesic curvature, thermodynamic equilibrium.]
\todo{setup and run dummy tests}

\subsection{Homogenous Absorbing Star}
\label{ssec:test_ab_star}
[Test described in~\cite[Sec.~3.2]{smit1997-two_moment}.]
\todo{Jerred: run test}

\subsection{Homogenous Scattering Star}
\label{ssec:test_sc_star}
\todo{maybe drop this test}
[Test presented in~\cite{humm1971-grey_transfer}
and described in~\cite[Sec.~9.1.1]{abdi2012-monte_carlo}.
Our version would be a point source embedded in a spherical distribution
of purely elastic-scattering material. It requires an analytical estimate
of $J$.]
\todo{formulate analytic $J$.}

\subsection{Post-Bounce Neutron Core}
\label{ssec:test_bounce_core}
[Standard radiation transport test described in~\cite{ocon2015-gr1d_with_nu},
and in \cite[App.~E.6]{fouc2015-m1_nsbh},
and in~\cite{abdi2012-monte_carlo}.]
\todo{Evan: provide initial data and $H^r(\varepsilon)$}
\todo{Jerred: setup and run test}

\subsection{Disk Comparison to M1}
\label{ssec:test_disk_comparison}
[Compute total and relative number and energy luminosities for a disk evolved
in one of~\cite{fouc2015-m1_nsbh, fouc2016-m1_nsns, fouc2016-m1_evolve_n}.
Expect agreement within factors of a few (?).]
\todo{code up moment integrals}
\todo{compute luminosities from M1}
\todo{compute luminosities from ray tracing}
